Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/paper.tex
minor changes

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first four months of the
study, our inspection process was exploratory.  Our goal in this phase
was to learn the extent to which \lo\ warnings could reveal bugs. We
realized that if we found that the ratio of bugs from \lo\ warnings
was rather low, we could focus our inspection efforts only on
\hi\ warnings. That finding would be important to reduce inspection
cost and guide future developments of this approach. To run this
experiment, we trained eight students in analyzing the warnings that
our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested students to update an ``owner'' column indicating who was
working on it, but we did not enforce an order on the warnings the
students should inspect. Recall from Section~\ref{sec:clusterization}
that we clustered \lo\ warnings in buckets. For that reason, we only
listed one \lo\ warning per representative class/bucket in the
spreadsheet. First, we explained the possible sources of false alarms
with examples and then we asked the students to use the following
procedure when finding a suspicious warning. Analyze the parts of the
spec related to the problem and, if still suspicious, look for
potential duplicates on the bug tracker of the affected engine using
related keywords. If none was reported, indicate in the spreadsheet
that that warning is potentially fault-revealing. We encouraged
students to use lithium~\cite{lithium} to minimize long test cases;
the tests from the Mozilla suite are often longer than others. Only
after the co-authors checked the potential bugs, a bug report was
filed.

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial four months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion. The rationale was to
give attention to each engine more uniformly, enabling more fair
comparison across engines. We repeated the following routine until
Aug. 22, 2018. We sampled five warnings associated with the group of a
given engine, analyzed these warnings, and moved to the group of
warnings associated with the next engine.

>>>>

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  Our goal in this phase
was to learn the extent to which \lo\ warnings could reveal bugs. We
realized that if we found that the ratio of bugs from \lo\ warnings
was rather low, we could focus our inspection efforts only on
\hi\ warnings. That finding would be important to reduce inspection
cost and guide future developments of this approach. To run this
experiment, we trained eight students in analyzing the warnings that
our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested students to update an ``owner'' column indicating who was
working on it, but we did not enforce an order on the warnings the
students should inspect. Recall from Section~\ref{sec:clusterization}
that we clustered \lo\ warnings in buckets. For that reason, we only
listed one \lo\ warning per representative class/bucket in the
spreadsheet. First, we explained the possible sources of false alarms
with examples and then we asked the students to use the following
procedure when finding a suspicious warning. Analyze the parts of the
spec related to the problem and, if still suspicious, look for
potential duplicates on the bug tracker of the affected engine using
related keywords. If none was reported, indicate in the spreadsheet
that that warning is potentially fault-revealing. We encouraged
students to use lithium~\cite{lithium} to minimize long test cases;
the tests from the Mozilla suite are often longer than others. Only
after the co-authors checked the potential bugs, a bug report was
filed.

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial three months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion. The rationale was to
give attention to each engine more uniformly, enabling more fair
comparison across engines. We repeated the following routine until
Aug. 22, 2018. We sampled five warnings associated with the group of a
given engine, analyzed these warnings, and moved to the group of
warnings associated with the next engine.
